Matching Bullets

### 2015-12-11 imaging-paper.Rnw
some more info on IBIS

@@

This work was funded in part by the Center for Statistics and Applications in Forensic Evidence (CSAFE).
\section{Conclusion}

\hh{Things we discussed}
\begin{enumerate}
\item the Hamby study only includes 35 bullets - this is not a particularly realistic scenario for automatic matching. Adding more non-matches into the mix is going to make things more realistic. 
\item The matching algorithm is sensitive to the parameter choices made. The distance between crosscuts (currently 25$\mu m$) to evaluate stability, as well as the cross-correlation factor (currently 0.9) we set as a minimum are affecting the final outcome. Another parameter is the amount of smoothing in identifying peaks and grooves (currently a window of 57.8375$\mu m$ is used, corresponding to a window of 17 values to the left and the right of an observation). While we tried to lay out in the paper the impact each of the parameter choices has on the matching, we are still far from an optimized scenario. 
\item reducing subjectivity: `the concept of counting striations is subjective and based on experience, but it does tend to be consistent within a single examiner' \cite{miller:1998}.
\item involve multiple crosscuts for each bullet in a match?
\item we get probabilities for matches. 
\item We don't have a solution for subclass characteristics
\end{enumerate}

Things to be dicussed in the future
\begin{enumerate}
\item reduce the stretch of crosscuts and match smaller pieces. This allows for both a more realistic scenario, as well as a quantification of the individuality of the segment.
\end{enumerate}
\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{references}

>>>>

\section{Conclusion}

\hh{Things we discussed}
\begin{enumerate}
\item the Hamby study only includes 35 bullets - this is not a particularly realistic scenario for automatic matching. Adding more non-matches into the mix is going to make things more realistic. 
\item The matching algorithm is sensitive to the parameter choices made. The distance between crosscuts (currently 25$\mu m$) to evaluate stability, as well as the cross-correlation factor (currently 0.9) we set as a minimum are affecting the final outcome. Another parameter is the amount of smoothing in identifying peaks and grooves (currently a window of 57.8375$\mu m$ is used, corresponding to a window of 17 values to the left and the right of an observation). While we tried to lay out in the paper the impact each of the parameter choices has on the matching, we are still far from an optimized scenario. 
\item reducing subjectivity: `the concept of counting striations is subjective and based on experience, but it does tend to be consistent within a single examiner' \cite{miller:1998}.

\item The analysis by Miller \cite{miller:1998} involved comparisons of 50 pairs of bullets against IBIS results (at the time consisting of 1,600 bullets of the same characteristics).

The feasibility of a database of ballistic images was evaluated in a 2008 report \cite{nap:2008} by the National Research Council. Part of the evaluation was based  on Integrated Ballistics Identification System (IBIS) -- to be precise, on the IBIS Heritage Line, which is based on 2d microscopic images. The findings of the report are

While microscopy allows some 3d effects (using different lighting and the innate ability of our eyes to move focus), in images this is reduced to a color shade of a pixel at best. This means that out of the top six features in Table~\ref{tab:importance}, only the number of matches and mismatches are available for a match, which vastly reduces the quality of automated matches.

\item involve multiple crosscuts for each bullet in a match?
\item we get probabilities for matches. 
\item We don't have a solution for subclass characteristics
\end{enumerate}

Things to be dicussed in the future
\begin{enumerate}
\item reduce the stretch of crosscuts and match smaller pieces. This allows for both a more realistic scenario, as well as a quantification of the individuality of the segment.
\end{enumerate}

@@

This work was funded in part by the Center for Statistics and Applications in Forensic Evidence (CSAFE).

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{references}
